Drivers of spatial synchrony in giant kelp populations

### 2021-05-14 paper/SupMat.tex
added outline of new stuff

In section \ref{sect:addquant}, we introduce several other metrics. These are all based on the distribution 
\begin{equation}
r_1=\ln[1-\delta+\delta \exp(b_1-b_2)] \label{r1distribution}
\end{equation}

@@

\noindent And since $(\beta_1, \beta_2)$ is distributed in the same way as our right-tail associated noise, this proves all metrics based on the distribution of $r_1$ \ref{r1distribution} are the same for left- and right-tail associated noise.

>>>>

In section \ref{sect:addquant}, we introduce several other metrics. These are all based on the distribution 
\begin{equation}
r_1=\ln[1-\delta+\delta \exp(b_1-b_2)]. \label{r1distribution}
\end{equation}

@@

\noindent And since $(\beta_1, \beta_2)$ is distributed in the same way as our right-tail associated noise, this proves all metrics based on the distribution of $r_1$ (\ref{r1distribution}) are the same for left- and right-tail associated noise.

\section{New Stuff}

Fixed number, base growth rate

\begin{equation}
\epsilon_i^0=\ln(1-\delta + \delta \frac{\bar B_i}{\bar B_j}) \label{null_i}
\end{equation}

\begin{equation}
\epsilon_i^E=\ln(1-\delta + \delta \frac{B_i}{\bar B_j}) -  \epsilon_i^0 \label{Evar}
\end{equation}

contribution of variance in E

\begin{equation}
\bar \epsilon_i^E=\EX(\epsilon_i^E) \label{Evar_mean}
\end{equation}

\begin{equation}
\epsilon_i^C=\ln(1-\delta + \delta \frac{\bar B_i}{B_j}) -  \epsilon_i^0 \label{Cvar}
\end{equation}

contribution of variance in C

\begin{equation}
\bar \epsilon_i^C=\EX(\epsilon_i^C) \label{Cvar_mean}
\end{equation}

\begin{equation}
\epsilon_i^{EC}=\ln(1-\delta + \delta \frac{B_i}{B_j}) -  [\epsilon_i^0 + \epsilon_i^E + \epsilon_i^C] \label{ECvar}
\end{equation}

interaction effect of both E and C varying

\begin{equation}
\bar \epsilon_i^{EC}=\EX(\ln(1-\delta + \delta \frac{B_i}{B_j})) -[\epsilon_i^0 +\bar \epsilon_i^E + \bar \epsilon_i^C] \label{ECvar_mean}
\end{equation}

\begin{equation}
\bar r_i=\EX(\ln(1-\delta + \delta \frac{B_i}{B_j}))\label{rbari}
\end{equation}

\begin{equation}
\bar r_i=\epsilon_i^0 +\bar \epsilon_i^E + \bar \epsilon_i^C + \bar \epsilon_i^{EC} \label{rbari_decomp}
\end{equation}

But some of $\bar \epsilon_i^{EC}$ comes from covariance between E and C and some comes from both varying.

\begin{equation}
\bar \epsilon_i^{(E\#C)}=\EX(\ln(1-\delta + \delta \frac{B_i}{B_j^{\#}})) -[\epsilon_i^0 +\bar \epsilon_i^E + \bar \epsilon_i^C] \label{ECvar_sharp}
\end{equation}

\begin{align}
\bar \epsilon_i^{(EC)}&=\bar \epsilon_i^{EC}-\bar \epsilon_i^{(E\#C)}\\
&= \EX(\ln(1-\delta + \delta \frac{B_i}{B_j}))-[\epsilon_i^0 +\bar \epsilon_i^E + \bar \epsilon_i^C]\\
&- \EX(\ln(1-\delta + \delta \frac{B_i}{B_j^{\#}})) +[\epsilon_i^0 +\bar \epsilon_i^E + \bar \epsilon_i^C]
\label{r_iSE}
\end{align}

checks out
